\section{Solution}
\label{sec:Solution}
% 1. What we're doing:
Our group will work to develop an application that is able to demonstrate the WebXR abilities. Specifically, we want to make use of VR controllers in our web application. Since WebVR is already well known and doesn’t make use of controllers, our job is to create an experience that you are able to interact with using WebXR.

% 2. How we're going to do it:
The goal is to include many common features that potential developers may use in trying to develop their own WebXR experiences so that, in the future, our work can be used as a reference. This website will eventually be hosted on Intel’s open source portal, 01.org. From there, people in the open source community can try out the technology and see the source code if they are interested in creating a web virtual reality or augmented reality project of their own. 

% 3. Why is VR the right choice for our project's content?
Research is an integral part in ensuring that the development process is smooth. As our client noted, we will need to research the best way create the VR experience before we begin development. Research will also need to be done on the benefits brought by adding AR or VR functionality to a website.

% 4. What will it look like:
% - What makes each project something that we'll be able to showcase WebXR through?
% Physics - Lots of controller interactions, example of progressive enhancement (basic physics equations -> physics playground)
Many ideas have been thrown around already. These include a physics simulation where users can explore the laws of physics on objects in the scene such as spheres. Users would be able to scale objects, throw them around, create tracks for testing physics and change the global physics values in the scene.

% Event Seating - Real life use case that could affect sales, Not as much controller interaction
Another proposed application was an event seating viewer. Users, while purchasing seating tickets for a sporting event or live show are often unsure about the view that their seats have. They could place themselves into a virtual reality environment where they could view a 3D model of the stadium or theatre from their chosen seat before purchase.

% Data Visualization - Lots of controller use, progressive enhancement (2d graph -> 3d graph with interactability)
Also discussed were Data Visualization applications. Some scatter plots and graphs are incredibly difficult to read when they incorporate gigantic amounts of data into a small 2D space. These graphs are often hard to visualize. VR makes data visualization easier because you are able to inspect the data in three dimensions. The additional dimension removes the clutter and restrictions of a 2D space, enhancing the user experience. Interaction with the scene can come in the form of scaling and rearranging the data.

% Battleship/Tower Defense - Good controller use, progressive enhancement (simple battleship -> awesome battleship)
Several games were proposed such as Battleship and Tower Defense. Everyone likes a good video game. So naturally a good solution for this problem is to provide some sort of VR gaming experience on the web.

Most of the proposed solutions were defined by how they are able to deliver an experience that the user cannot normally get without many additional steps. Most important is how each project is able to deliver some impact to those who experience them. The goal of this project is to deliver an experience that garners interest in the WebXR platform and its capabilities.

As we do this research, we will work with our client to develop the actual app we are creating as an example to the community. This enables more content creation because the web has great scaling and is easily accessible to millions of internet user instantly. In this respect, we will get some degree of freedom in choosing the deliverable project. 
